Rotational Spectral Unmixing of Exoplanets:\\Degeneracies between Surface Colors and Geography

### 2017-03-11 paper/main.tex
approximate location of colors of ocean, soil, cloud projected onto EPOXI PC plane

Given that any vertices in the PC plane that enclose the trajectory/-ies can be a solution, the choice of the solution critically depends on the prior probability distribution. 
% Thus, we need to be careful about the implicit assumptions that are made  
With no assumptions or information on the spectral albedo of the surface types or geography, it may be reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type. 
%While such an assumption does not seem to work at all to choose the surface types, it does put some constrains. 
While such an assumption does not uniquely specify the colors of all $K$ surface types, it does offer constraints due to the relative light curve trajectory within the permitted region. 
%This is because of the relative configuration of the trajectory and the permitted region. 
For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the bottom left corner of the permitted region (white triangle); this is consistent with the fact that one of the input albedo spectra (ocean) resides there. \memoJLY{and is a dominant surface type...?}

@@

\memoYF{Have to do with regularization on the maps, but how should we proceed without doing MCMC with both $f_{lk}$ and $s_{kj}$ being fitting parameters? I could operate $W^{+}_{li} \fast_{ik}$ to find $f_{lk}$ with condition (\ref{eq:f_range}) and (\ref{eq:f_sum}); this itself is a bounded linear inversion problem and thus needs some minimization. Also, without regularization, I tend to find scattered $f_{lk}$, perhaps because of the instability of inverse matrix??. }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbh!]
    \begin{center}
	\includegraphics[width=\hsize]{raddata_2_PCplane_noreg.pdf}
    \end{center}
    \caption{PC plane from EPOXI observation of June 2008. }
\label{fig:EPOXI}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this case, the trajectory of planetary light curves is away from the boundary because the color variations of the real Earth are muted by the cloud cover \memoYF{True?}. 
Consequently, we do not see three peaks but a spectrum of the potential. 
Nevertheless, we are likely to find one surface type near the upper right part of the allowed region.

@@

\memoYF{Problem in inverse matrix...!}

>>>>

Given that any vertices in the PC plane that enclose the trajectory/-ies can be a solution, the choice of the solution critically depends on the prior probability distribution. 
% Thus, we need to be careful about the implicit assumptions that are made  
With no assumptions or information on the spectral albedo of the surface types or geography, it may be reasonable to assume that any points in the PC plane except for the inhibited regions are equally likely to correspond to a surface type. 
%While such an assumption does not seem to work at all to choose the surface types, it does put some constrains. 
While such an assumption does not uniquely specify the colors of all $K$ surface types, it does offer constraints due to the relative light curve trajectory within the permitted region. 
%This is because of the relative configuration of the trajectory and the permitted region. 
For example, in Figure \ref{fig:trajectory}, in order to enclose the trajectory with three surface types within the permitted region, we must have at least one point near the bottom left corner of the permitted region (white triangle); this is consistent with the fact that one of the input albedo spectra (ocean) resides there.

@@

%\memoYF{Have to do with regularization on the maps, but how should we proceed without doing MCMC with both $f_{lk}$ and $s_{kj}$ being fitting parameters? I could operate $W^{+}_{li} \fast_{ik}$ to find $f_{lk}$ with condition (\ref{eq:f_range}) and (\ref{eq:f_sum}); this itself is a bounded linear inversion problem and thus needs some minimization. Also, without regularization, I tend to find scattered $f_{lk}$, perhaps because of the instability of inverse matrix??. }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbh!]
    \begin{center}
	\includegraphics[width=\hsize]{raddata_2_PCplane_noreg.pdf}
    \end{center}
    \caption{PC plane from EPOXI observation of June 2008. \memoYF{I have not computed the exact location of ocean, soil, or clouds, but roughly, ocean is probably around (-0.2, 0.4), soil is around (0.5, 0.0), and cloud is around (0.1,-0.5).}}
\label{fig:EPOXI}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In this case, the trajectory of planetary light curves is away from the boundary because the color variations of the real Earth are muted by the cloud cover. 
Consequently, we do not see three peaks but a spectrum of the potential. 
Nevertheless, we are likely to find one surface type near the upper right part of the allowed region.

@@

%\memoYF{Problem in inverse matrix...!}
